Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-05 ms.Rnw
Changed renamed functions
Changed the way model 2 is fit

# Evaluate and sum objective functions to get total model likelihood
mod2_ll <- -(epi_ofun(par = h2_fit$epi_params) + end_ofun(par = h2_fit$end_params))

@@

# Create Lee et al (2020a) version of model 3 on sub-data
lee3_sub <- haiti3()

@@

lee3_all <- haiti3(start_time = "2010-10-23")

@@

      \Sexpr{myround(52/h2_fit$end_params["Delta"],1)}

>>>>

mod2_epi_ll <- -epi_ofun(par = h2_fit$epi_params)
mod2_end_ll <- -end_ofun(par = h2_fit$end_params)

mod2_ll <- mod2_epi_ll - sum(apply(log(h2_epi@data + 1), 1, sum)) + (mod2_end_ll - sum(apply(log(h2_end@data + 1), 1, sum, na.rm = TRUE)))

# Evaluate and sum objective functions to get total model likelihood
# mod2_ll <- -(epi_ofun(par = h2_fit$epi_params) + end_ofun(par = h2_fit$end_params))

@@

# Create Lee et al (2020a) version of model 3 on sub-data
lee3_sub <- haiti3_lee_et_al()

@@

lee3_all <- haiti3_lee_et_al(start_time = "2010-10-23")

@@

      \Sexpr{signif(52/h2_fit$end_params["Delta"],1)}
